Supporting Information

### 2015-08-24 ms.Rmd
run GSEA only on expressed genes

@@

**`r I(pasteLabel("Figure ", figCount, "f_gsea"))`**. Geneset enrichment analysis (GSEA) for transcription factor families. Test statistics were calculated on a matrix of Log~2~(fold change) values between each sample and the other three samples. A positive test statistic indicates enrichment and a negative statistic indicates depletion. Although some test statistics had low *p*-values none were less than 0.10 after Benjamini-Hochberg correction.

>>>>

The patterns are not completely representative of all members of each gene family. For example, there are several MADS genes that have lower expression in the SM than in the RM, but expressed MADS genes were detected at a higher level overall in SM. Nevertheless, there are some notable modes of expression shared between different TF families. Several TF families, including bZIP and ABI3VP1, are strongly expressed in RM and lower in the other meristem types. Another group incluiding Squamosa binding proteins and Jumonji transcription factors is more weakly expressed in the RM but enriched in the PBM, suggesting a switch of expression between these two meristem types. Correspondingly, the difference between the RM and PBM samples was the most remarkable in the GSEA.

@@

**`r I(pasteLabel("Figure ", figCount, "f_gsea"))`**. Geneset enrichment analysis (GSEA) for transcription factor families. Test statistics were calculated on a matrix of Log~2~(fold change) values for expressed TF family members between each sample and the other three samples. A positive test statistic indicates enrichment and a negative statistic indicates depletion. Although some test statistics had low *p*-values none were lower than 0.10 after Benjamini-Hochberg correction.

### 2015-08-24 si.Rmd
implemented gsea and gsea figure
run GSEA only on expressed genes

**`r I(pasteLabel("Figure S", s_figCount, "sf_pca"))`**: Principal components analysis of transformed read counts for each library. The two libraries made from degraded RNA did not appear to cluster with other libraries (see `r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`), suggesting that the use of degraded RNA had an effect on the quantification of read counts. For this reason these two libraries were not included in subsequent analyses.

@@

**`r I(pasteLabel("Figure S", s_figCount, "sf_mfuzzCentroids"))`**: Minimum centroid distance for 2–`r maxClust` cluster cores (*c*). Eight cluster cores were used because the rate of change of the minimum centroid distance over *c* decreases after *c* = 8.

>>>>

**`r I(pasteLabel("Figure S", s_figCount, "sf_pca"))`**: Principal components analysis of transformed read counts for each library. The two libraries made from degraded RNA did not cluster with other libraries (see `r I(pasteLabel("Table S", s_tableCount, "st_libStats"))`), suggesting that the use of degraded RNA had an effect on the quantification of read counts. For this reason these two libraries were not included in subsequent analyses.

@@

**`r I(pasteLabel("Figure S", s_figCount, "sf_mfuzzCentroids"))`**: Minimum centroid distance for 2–`r maxClust` cluster cores (*c*). Eight cluster cores were used because the rate of change of the minimum centroid distance over *c* decreases after $c = 8$.
